### 2025-07-09 intro.qmd
20250708 - track chunk execution times
20250708 - videos and quotes

@@

"*This material probably won't win you fantasy football championships.
You could take what we learn and apply it to fantasy football and you might become 5 percent more likely to win.
Or...
Consider the broader relevance of this.
You could learn data analysis and figure out ways to apply it to other systems.
And you could be making a six-figure salary within the next five years.*"
– Benjamin Motz, Ph.D.

>>>>

::: {#fig-video-motz}

@@

> "*This material probably won't win you fantasy football championships.
> You could take what we learn and apply it to fantasy football and you might become 5 percent more likely to win.
> Or...
> Consider the broader relevance of this.
> You could learn data analysis and figure out ways to apply it to other systems.
> And you could be making a six-figure salary within the next five years.*" – [Benjamin Motz, Ph.D.](#fig-video-motz) [@NFL2014]
